---
title: "Part 1"
author: "Kahvi Patel"
output: html_document
---

#### Loading Libraries
```{r echo = T, results = 'hide', message=FALSE, warning=FALSE}
library(tidyverse)
library(viridis)
library(scales)
```

### Data Import and Cleaning
```{r echo = T, results = 'hide', warning=FALSE}
setwd("~/Desktop/Spring 2019/STAT 123/Final Project")

ds <- read_csv("Data/919report_data.csv")

# Functions
clean.up = function(x) {
  if (is.na(x)) {
    x <- FALSE
  } else if (x == 0) {
    x <- FALSE
  } else {
    x <- TRUE
  }
}

# Fix and seperate Time
ds$Time = sapply(strsplit(as.character(ds$Time), " "), tail, n = 1)
ds = ds %>%
  mutate(Time=hms::as.hms(Time))

# Time of Day Column
ds = ds %>%
  mutate(Time_Of_Day = 
           ifelse((Time <= 12*60*60 & Time >= 5*60*60), "Morning", 
           ifelse((Time <= 17*60*60 & Time > 12*60*60), "Afternoon", 
           ifelse((Time < 22*60*60 & Time > 17*60*60), "Evening", "Night"))))

# Reorder, rename Columns
ds <- ds[c(1,2,3,43,4:42)]
colnames(ds)[17] <- "Attended By: Fire"
colnames(ds)[42] <- "Event Location: Snack Bar"

# Tranforms with semicolon
for (i in c(12:17, 19:26, 30:42)) {
  ds[i] <- apply(ds[i], MARGIN = 1, FUN = clean.up)
  ds[i] <- transform(ifelse(ds[i] == TRUE, paste(str_split(colnames(ds)[i], ": ")[[1]][2]), NA))
}

# Transforms with no semicolon
for (i in c(11, 27:29)) {
  ds[i] <- apply(ds[i], MARGIN = 1, FUN = clean.up)
  ds[i] <- transform(ifelse(ds[i] == TRUE, paste(colnames(ds)[i]), NA))
}

# Unite transformed Columns
ds <- unite(ds, col = "Incident_Type", matches("Incident"), sep=",")
ds$Incident_Type <- gsub("NA[,]?","", ds$Incident_Type)
ds$Incident_Type <- gsub("^$", NA, ds$Incident_Type)

ds <- unite(ds, col = "Attended_By", matches("Attended"), sep=",")
ds$Attended_By <- gsub("NA[,]?","", ds$Attended_By)
ds$Attended_By <- gsub("^$", NA, ds$Attended_By)

ds <- unite(ds, col = "Init_Call", matches("Call"), sep=",")
ds$Init_Call <- gsub("NA[,]?","", ds$Init_Call)
ds$Init_Call <- gsub("^$", NA, ds$Init_Call)

ds <- unite(ds, col = "Location", matches("Event"), sep=",")
ds$Location <- gsub("NA[,]?","", ds$Location)
ds$Location <- gsub("^$", NA, ds$Location)

ds = ds %>%
  separate(Incident_Type, "Incident Type", sep = ",", remove = TRUE) %>%
  separate(Attended_By, "Attended By", sep = ",", remove = TRUE) %>%
  separate(Init_Call, "Initial Call", sep = ",", remove = TRUE) %>%
  separate(Location, "Location", sep = ",", remove = TRUE)

ds$Location <- factor(ds$Location)

ds$Location <- fct_infreq(ds$Location)

```

### 1. Summary statistics

```{r}
summary(ds)
```

## 2. Are there more incidents at the end of the day?
Yes. There are more incidents in the afternoon/evening than in the morning.

```{r message=FALSE, warning=FALSE}
ggplot(data.frame(ds$Time_Of_Day), aes(x=ds$Time_Of_Day)) +
  geom_bar() + 
  xlab("Time of Day") +
  ylab("# of Incidents")

ggplot(data.frame(ds$Time), aes(x=as.POSIXct(strptime(ds$Time, format="%H:%M:%S")))) +
  geom_histogram() +
  xlab("Time") + 
  ylab("# of Incidents") +
  scale_x_datetime(breaks = date_breaks("3 hour"), labels = date_format("%I:%M %p"))
```

## 3. Number of Overdose Calls to ambulance

```{r}
overdose_calls <- sum(ds$Overdose == "Overdose", na.rm = TRUE)
print(overdose_calls)
```

## 4. Numbers of calls to first responders

```{r}
calls <- sum(ds$`Emergency Services Required` == "Emergency Services Required", na.rm = TRUE)
print(calls)
```

## 5. Is there a correlation between the time of incident and the site of incident?

It seems like there are more incidents after 5PM when the patient is a Drop-In. There are more incidents in the night when the patient is in the Courtyard. Aside from those two locations, the frequency of incidents in the other locations is moderately constant throughout the day.

```{r message=FALSE, warning=FALSE}
ggplot(data = subset(ds, !is.na(Location)), aes(x = as.POSIXct(strptime(Time, format="%H:%M:%S")),
               color = factor(Location))) + 
  geom_freqpoly() +
  xlab("Time") +
  ylab("# of Incidents") +
  scale_x_datetime(breaks = date_breaks("4 hour"), labels = date_format("%I:%M %p")) +
  labs(color = "Location")

ggplot(data = subset(ds, !is.na(Location)), aes(x = as.POSIXct(strptime(Time, format="%H:%M:%S")), 
               y = Location,
               color = factor(Location))) + 
  geom_point() +
  scale_x_datetime(breaks = date_breaks("4 hour"), labels = date_format("%I:%M %p")) +
  xlab("Time") +
  guides(color = FALSE)
```