---
title: "Part 2"
author: "Kahvi Patel"
output: html_document
---

*Son et al. (2003) studied 100 caregivers of older adults with dementia in Seoul, South Korea. The
dependent variable was caregiver burden measured by the Korean Burden Inventory (KBI). Scores ranged from 28 to 140 with higher scores indicating higher burden. Explanatory variables were indexes that measured the following:

ADL: (X1) total activities of daily living (low scores indicate that the elderly perform activities independently).

MEM: (X2) memory and behavioral problems (higher scores indicate more problems).

COG: (X3) cognitive impairment (lower scores indicate a greater degree of cognitive impairment).

## Data Import and Cleaning
```{r}
#read in .csv file
df <- read.csv('Data/stat123_regression.csv')  
```

### 1. After reading the data into R using the read.csv function, provide summary of the data. Comment on your results and especially on any unusual features in the data.

```{r}
summary(df)
```
### 2. Produce the boxplot of ADL. Comment. Are there any outliers?

No, It doesn't look like there are any outliers.

```{r}
boxplot(df$ADL)
```

### 3. Produce the scatterplots of Y and the X’s. Comment. Is a linear model appropriate for this data? Why or why not? Are the X’s correlated amongst themselves.

A linear model is not appropriate for the regression variables ADL or COG. However, MEM looks to be somewhat linear in its behaviour according to the scatterplot.

```{r}
plot(df$ADL, df$KBI,
     main='KBI vs ADL',
     xlab="total activities of daily living", ylab="Korean Burden Inventory")

plot(df$MEM, df$KBI,
     main='KBI vs MEM',
     xlab="memory and behavioral problems", ylab="Korean Burden Inventory")

plot(df$COG, df$KBI,
     main='KBI vs COG',
     xlab="cognitive impairment", ylab="Korean Burden Inventory")
```

### 4. Fit univariable linear models, Y versus Xi for each of the three X regressor variables. 
a. What are the estimated regression models?
b. Compare the univariable models above.
c. Check the fit of the models and comment.
d. Explain each of the estimated regression parameters (except the intercept) in words.