---
title: "UVic Engin/Math co-op salaries"
author: "Fan Wu"
output: pdf_document
---

Analyze Co-op monthly salaries for UVic Engineering/Math students, undergraduate and graduate students.
Some salaries were mistakenly entered as weekly salaries and many were not entered 
and are zero.  Remove the zero salaries.  Assume that salaries <$1000 are weekly salaries and multiply them by four.

Notes from class: 

1. Students working abroad, for example in the U.S.A., may not have converted their
salaries to Canadian dollars.  

2. Some students may have entered their biweekly/bimonthly salary since many are paid 
at those times.

##Data preparation and descriptives##

```{r}
#read in .csv file
salary<-read.csv('../Data/salaryInfo.csv')  
summary(salary)

#convert to short names
names(salary)
names(salary)<-c('Term','WTNum','GR.UG','SalMonthRaw')  
#remove the zero salaries
salarynz<-subset(salary, SalMonthRaw!=0)   
summary(salarynz)

hist(salarynz$SalMonthRaw)

salarynz[salarynz$SalMonthRaw<1000,]
salarynz$SalMonth<-salarynz$SalMonthRaw
#assume that salaries <$1000 are weekly
salarynz$SalMonth[salarynz$SalMonthRaw<1000]<-
     salarynz$SalMonthRaw[salarynz$SalMonthRaw<1000]*4   
summary(salarynz)

hist(salarynz$SalMonth)
summary(salarynz$WTNum)
#remove the student with unknown workterm
salarynz[salarynz$WTNum=='N/A',]
salarynz<-salarynz[salarynz$WTNum!='N/A',]  
summary(salarynz)

hist(salarynz$SalMonth, main='Monthly Engin/Math Co-op salaries', 
     xlab='Monthly salary $')
```




```{r}



#extract out WorkTerm 1 salaries 
ywt1<-subset(salarynz,salarynz$WTNum=='W-1')
summary(ywt1)
ywt1<-ywt1[,-4]
summary(ywt1)
ywt1$WTNum<-factor(ywt1$WTNum)
rownames(ywt1)<-NULL
summary(ywt1)

#analyze WorkTerm 1 salaries
dim(ywt1)
n<-dim(ywt1)[1]
summary(ywt1$SalMonth)

salarynz %>%
  filter(WTNum %in% c("W-1","W-2")) %>%
  ggplot(aes(x=SalMonth)) +
  geom_histogram() + 
  facet_wrap(~WTNum)

hist(ywt1$SalMonth, main='Work Term 1 Salaries', xlab='Monthly Salaries $')


```

-----------------------------

###Regression analysis of Salaries versus Work Term number###


```{r}
summary(salarynz)
summary(salarynz$WTNum)
#there is an un-used level "N/A" which we need to remove
salarynz$WTNum<-factor(salarynz$WTNum)
summary(salarynz$WTNum)
salarynz$WTNumN<-as.numeric(salarynz$WTNum)
summary(salarynz$WTNumN)




#Graph the data; side-by-side boxplots are one of my favourites

boxplot(salarynz$SalMonth~salarynz$WTNum, xlab='Work Term Number',ylab='monthly salary',
     main='Monthly Salary versus Work Term Number')

plot(salarynz$WTNumN, salarynz$SalMonth, xlab='Work Term Number',ylab='monthly salary',
     main='Monthly Salary versus Work Term Number')
##############################################################################################

Sal.lm<-lm(SalMonth~WTNumN, data=salarynz)
summary(Sal.lm)

####################################
##Check the model 

plot(Sal.lm,which=1:2)

# 1: Residuals VS Fitted values plot: Any any special pattern, we will conclude that the residuals have a constance varaince.
# 2: Normal Q-Q plot: if all of scatters are roughly on a straight line, we will conclude the residuals follow a normal distribution.  


###############################summary(cars)
dim(cars)   #shape of database
head(cars)   #look at top rows
tail(cars)   #look at bottom rows
sd(cars$speed)  #standard deviation of speed
sd(cars$dist)   #standard deviation of dist


```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
plot(cars$speed, cars$dist,
     main='Scatterplot Distance vs Speed',
     xlab='speed', ylab='distance')
boxplot(cars$speed, main='Boxplot of Speed')
hist(cars$speed, main='Histogram of Speed')
cars.lm <- lm(dist~speed, data=cars)   #lm fits a linear model dist = beta_0 + beta_1 speed
cars.lm                                # display the estimates of beta_0  and beta_1
summary(cars.lm)


cars.lmconf <- confint(cars.lm)         #95% confidence intervals for beta_0, beta_1
cars.lmconf
plot(cars$speed, cars$dist,
     main='Scatterplot Distance vs Speed',
     xlab='speed', ylab='distance')
abline(cars.lm)  #adds LS fitted line

```


